Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-02 manuscript.Rmd
ready to start modeling

@@

```{r map_travel_timne}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)

travel_time_sf %>% filter(year == 2017, month == 1, week == 4)%>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	geom_sf(data = dc_roads) +
	theme_map +
	scale_fill_viridis_c(direction = -1)
```

```{r map_acs}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = med_incomeE)) +
	theme_map +
	scale_fill_viridis_c()
```

```{r}
travel_time_sf %>% 
  mutate(state = substr(geo2010, start = 1, stop = 2)) %>%
  mutate(tract_number = substr(geo2010, start = 10, stop = 1000)) %>%
```

```{r map_acs}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = blackE)) +
	theme_map +
	scale_fill_viridis_c()
```

```{r map_acs}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = car_transitE)) +
	theme_map +
	scale_fill_viridis_c()
```

>>>>

```{r centroids}
dc_acs_tracts$centroids <- st_centroid(st_geometry(dc_acs_tracts), of_largest_polygon)

plot(st_geometry(dc_acs_tracts), border="grey")
plot(dc_acs_tracts$centroids, add=TRUE, col="blue", cex = 0.3)
```

@@

```{r map_travel_time}
map_lims <- st_bbox(dc_acs_tracts)

travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time), lwd=0.2) +
	geom_sf(data = travel_time_sf$centroids, cex = 0.5) +
	scale_fill_viridis_c(direction = -1)

travel_time_sf %>% filter(year == 2017, month == 1, week == 4) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time), lwd=0.2) +
	geom_sf(data = dc_roads, color = "white", lwd=0.2) +
	geom_sf(data = metro_line, color = "black", lwd=0.2) +
	theme_map +
  coord_sf(xlim = c(map_lims["xmin"], map_lims["xmax"]), ylim = c(map_lims["ymin"], map_lims["ymax"])) +
	scale_fill_viridis_c(direction = -1)
```

```{r map_acs}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = med_incomeE)) +
	theme_map +
	scale_fill_viridis_c()

travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = blackE)) +
	theme_map +
	scale_fill_viridis_c()

travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = car_transitE)) +
	theme_map +
	scale_fill_viridis_c()
```
